Gaussian Process regression for astronomical time-series

### 2022-08-14 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{table}[ht]
  \caption{Some kernel functions commonly used in the astrophysics literature}
  \label{tab:kernels}
  \begin{center}
    \begin{tabular}{@{}l|l@{}}
      \hline
      Name                           &  Representation$^{\rm a}$                                    \\
      \hline
      Constant kernel                & $\sigma^2$                                                     \\
      Exponential Squared$^{\rm b}$  & $e^{-\tau^2/2}$                                              \\
      Exponential$^{\rm c}$          & $e^{-\tau}$                                                  \\
      Mat\'ern-3/2                   & $\left(1 + \sqrt{3}\tau\right)e^{-\sqrt{3}\tau}$             \\
      Mat\'ern-5/2                   & $\left(1 + \sqrt{5}\tau +5\tau^2/3\right)e^{-\sqrt{5}\tau}$  \\
      Cosine                         & $\cos \tau$                                                  \\
      Exponential Sine Squared       & $\exp\left(-\gamma\sin^2\pi\tau\right)$                      \\
      Stochastic Harmonic Oscillator$^{\rm d}$ & $\cos\left(\sqrt{1-\beta^2}\tau\right) + \frac{\beta}{\sqrt{1-\beta^2}}\sin\left(\sqrt{1-\beta^2}\tau\right)$                          \\
      \hline
    \end{tabular}
  \end{center}
  \begin{tabnote}
    $^{\rm a}$in each case, $\tau$ is defined as $\tau = \left|t_i - t_j\right| / \lambda$, where the timescale $\lambda$ is a hyperparameter, and any other undefined Greek letters are also hyperparameters;
    $^{\rm b}$``radial basis function'';
    $^{\rm c}$``damped random walk'' or ``Mat\'ern-1/2'';
    $^{\rm d}$\citet{celerite}.
  \end{tabnote}
\end{table}

>>>>

\begin{table}[ht]
  \caption{Some kernel functions commonly used in the astrophysics literature}
  \label{tab:kernels}
  \begin{center}
    \begin{tabular}{@{}l|l@{}}
      \hline
      Name                           &  Representation$^{\rm a}$                                    \\
      \hline
      Constant kernel                & $\sigma^2$                                                     \\
      Exponential Squared$^{\rm b}$  & $e^{-\tau^2/2}$                                              \\
      Exponential$^{\rm c}$          & $e^{-\tau}$                                                  \\
      Mat\'ern-3/2                   & $\left(1 + \sqrt{3}\tau\right)e^{-\sqrt{3}\tau}$             \\
      Mat\'ern-5/2                   & $\left(1 + \sqrt{5}\tau +5\tau^2/3\right)e^{-\sqrt{5}\tau}$  \\
      Cosine                         & $\cos \tau$                                                  \\
      Exponential Sine Squared       & $\exp\left(-\gamma\sin^2\pi\tau\right)$                      \\
      Stochastic Harmonic Oscillator$^{\rm d}$ & $\cos\left(\sqrt{1-\beta^2}\tau\right) + \frac{\beta}{\sqrt{1-\beta^2}}\sin\left(\sqrt{1-\beta^2}\tau\right)$                          \\
      \hline
    \end{tabular}
  \end{center}
  \begin{tabnote}
    $^{\rm a}$in each case, $\tau$ is defined as $\tau = \left|t_i - t_j\right| / \lambda$, where the timescale $\lambda$ is a hyperparameter, and any other undefined Greek letters are also hyperparameters;
    $^{\rm b}$``radial basis function'';
    $^{\rm c}$``Ornstein-Uhlenbeck'', ``damped random walk'' or ``Mat\'ern-1/2'';
    $^{\rm d}$\citet{celerite}.
  \end{tabnote}
\end{table}

\begin{figure}[ht]
  \centering
  \script{samples.ipynb}
  \begin{minipage}[t]{0.3\linewidth}
    \includegraphics[width=\linewidth]{figures/samples1.pdf}
  \end{minipage} \hfill
  \begin{minipage}[t]{0.3\linewidth}
    \includegraphics[width=\linewidth]{figures/samples2.pdf}
  \end{minipage} \hfill
  \begin{minipage}[t]{0.3\linewidth}
    \includegraphics[width=\linewidth]{figures/samples3.pdf}
  \end{minipage}
  \caption{Prior samples for three different classes of kernel functions: (a) exponential, (b) Mat\'ern-3/2, and (c) exponential squared.
  In each sub-figure, the length scale $\lambda$ of the kernel increases from left to right, and the amplitude $\alpha$ increases from top to bottom.
  One thing to notice in this figure is that these kernel functions differ in their smoothness properties.
  Specifically, the exponential kernel is not mean-square differentiable, while the exponential squared kernel is infinitely differentiable.
  This can be seen qualitatively in this figure.}
  \label{fig:samples}
\end{figure}
